Final project

### 2021-12-17 final_project.Rmd
correct cp

```{r}
olsrr::ols_mallows_cp(fit_back_without,trans_fit) #-14.65
olsrr::ols_mallows_cp(trans_fit_without,trans_fit)# -10.59
olsrr::ols_mallows_cp(fit_adjr_without,trans_fit) #-14.49
```

>>>>

```{r}
olsrr::ols_mallows_cp(fit_back_without,trans_fit_without) # 7.047
olsrr::ols_mallows_cp(trans_fit_without,trans_fit_without)# 11
olsrr::ols_mallows_cp(fit_adjr_without,trans_fit_without) # 7.102
```
